Raw Data Comparison

### 2019-09-11 Raw Data Comparison.Rmd
...

@@

@@

t.per.pt.scale = as_tibble(t(apply(as.matrix(training.tiles[,-1]), 1, scale, center=T, scale=T))) %>% add_column('sample'=training.tiles$Sample, .before=1)
colnames(t.per.pt.scale) = colnames(training.tiles)

v.per.pt.scale = as_tibble(t(apply(as.matrix(val.tiles[,-1]), 1, scale, center=T, scale=T))) %>% add_column('sample'=val.tiles$Sample, .before=1)
colnames(v.per.pt.scale) = colnames(val.tiles)

@@

t.dist = tile.dist.measure(t.per.pt.scale) %>% mutate(cohort='train')
v.dist = tile.dist.measure(v.per.pt.scale) %>% mutate(cohort='val')

@@

@@

# FPR is ~40% still
nrow(preds %>% filter(Status == 'NP' & Risk == 'High'))/nrow(preds %>% filter(Status == 'NP'))

# FNR is still over 50% in the old progressors as well
nrow(preds %>% filter(Status == 'P' & Risk == 'Low' & !grepl('OCCAMS',`Hospital Research ID`)))/nrow(preds %>% filter(Status == 'P' &  !grepl('OCCAMS',`Hospital Research ID`)))
```

@@

# FNR is still over 50% in the old progressors as well
nrow(preds %>% filter(Status == 'P' & Risk == 'Low' & !grepl('OCCAMS',`Hospital Research ID`)))/nrow(preds %>% filter(Status == 'P' &  !grepl('OCCAMS',`Hospital Research ID`)))
```

>>>>

files = list.files('~/Data/BarrettsProgressionRisk/Analysis/multipcf_perPatient/', 'arms_cleaned', recursive=T, full.names = T)
training.arms = do.call(bind_rows, purrr::map(files, function(f) {
  read_tsv(f,col_types=c(.default=col_double()))
})) %>% dplyr::rename('Sample' = 'X1')

@@

files = list.files('~/Data/BarrettsProgressionRisk/Analysis/validation/multipcf/', 'arm_tiles', recursive=T, full.names = T)
val.arms = do.call(bind_rows, purrr::map(files, function(f) {
  read_tsv(f,col_types=c(.default=col_double()))
})) %>% dplyr::rename('Sample' = 'X1')

@@

t.per.pt.scale = as_tibble(t(apply(as.matrix(training.tiles[,-1]), 1, scale, center=T, scale=T))) %>% add_column('sample'=training.tiles$Sample, .before=1)
colnames(t.per.pt.scale) = colnames(training.tiles)
t.arm.pp.scale = as_tibble(t(apply(as.matrix(training.arms[,-1]), 1, scale, center=T, scale=T))) %>% add_column('sample'=training.arms$Sample, .before=1)
colnames(t.arm.pp.scale) = colnames(training.arms)

v.per.pt.scale = as_tibble(t(apply(as.matrix(val.tiles[,-1]), 1, scale, center=T, scale=T))) %>% add_column('sample'=val.tiles$Sample, .before=1)
colnames(v.per.pt.scale) = colnames(val.tiles)
v.arm.pp.scale = as_tibble(t(apply(as.matrix(val.arms[,-1]), 1, scale, center=T, scale=T))) %>% add_column('sample'=val.arms$Sample, .before=1)
colnames(v.arm.pp.scale) = colnames(val.arms)

@@

```{r}
t.dist = tile.dist.measure(t.per.pt.scale) %>% mutate(cohort='train')
v.dist = tile.dist.measure(v.per.pt.scale) %>% mutate(cohort='val')

gridExtra::grid.arrange(
  ggplot(bind_rows(t.dist, v.dist), aes(cohort, mean, group=cohort, fill=cohort)) + 
    geom_jitter(width=0.1) + geom_violin(alpha=0.5) + theme(legend.position = 'none') +
    labs(title='Mean'),
  ggplot(bind_rows(t.dist, v.dist), aes(cohort, sd, group=cohort, fill=cohort)) + 
    geom_jitter(width=0.1) + geom_violin(alpha=0.5) + theme(legend.position = 'none') +
    labs(title='SD'), 
  ncol=2, top='Per bin tiled values on per-pt scaled')
```

After the arm segments have been subtracted as well.
```{r}

t.pp.scale = BarrettsProgressionRisk:::subtractArms(as.matrix(t.per.pt.scale[,-1]), as.matrix(t.arm.pp.scale[,-1])) %>% as_tibble %>% add_column('Sample' = 'x', .before=1)
v.pp.scale = BarrettsProgressionRisk:::subtractArms(as.matrix(v.per.pt.scale[,-1]), as.matrix(v.arm.pp.scale[,-1]))  %>% as_tibble %>% add_column('Sample' = 'x', .before=1)

t.dist = tile.dist.measure(t.pp.scale) %>% mutate(cohort='train')
v.dist = tile.dist.measure(v.pp.scale) %>% mutate(cohort='val')

@@

```{r}
preds = do.call(bind_rows, purrr::map(
  list.files('~/Data/BarrettsProgressionRisk/Analysis/validation/multipcf/predictions_per_pt_scale/0.9/', pattern='predictions.tsv', recursive = T, full.names = T), 
  function(f) read_tsv(f, col_types = 'cddcccccccc'))) %>% mutate(Endoscopy = as.Date(Endoscopy)) %>% dplyr::select(-`Path Notes`) %>% mutate(`Hospital Research ID` = str_replace_all( str_remove_all(`Hospital Research ID`, " "), '/', '_'))

# Non progressors
# FPR is ~40% still
fpr = round(nrow(preds %>% filter(Status == 'NP' & Risk == 'High'))/nrow(preds %>% filter(Status == 'NP')),2)

preds %>% dplyr::filter(Status == 'NP') %>% group_by(Risk) %>% tally() %>% spread(Risk, n) %>% 
  kable(caption=paste0('NP risk predictions, FPR=',fpr)) %>% kable_styling(full_width = F)

# Progressors
# FNR is still over 50% in the old progressors as well
fnr = round(nrow(preds %>% filter(Status == 'P' & Risk == 'Low' & !grepl('OCCAMS',`Hospital Research ID`)))/nrow(preds %>% filter(Status == 'P' &  !grepl('OCCAMS',`Hospital Research ID`))),2)

preds %>% dplyr::filter(Status == 'P' & !grepl('OCCAMS',`Hospital Research ID`)) %>% group_by(Risk) %>% tally() %>% spread(Risk, n) %>% 
  kable(caption=paste0('P risk predictions, FNR=',fnr)) %>% kable_styling(full_width = F)

@@

# Non progressors
# FPR is ~40% still
fpr = round(nrow(preds %>% filter(Status == 'NP' & Risk == 'High'))/nrow(preds %>% filter(Status == 'NP')),2)

preds %>% dplyr::filter(Status == 'NP') %>% group_by(Risk) %>% tally() %>% spread(Risk, n) %>% 
  kable(caption=paste0('NP risk predictions, FPR=',fpr)) %>% kable_styling(full_width = F)

# Progressors
# FNR is still over 50% in the old progressors as well
fnr = round(nrow(preds %>% filter(Status == 'P' & Risk == 'Low' & !grepl('OCCAMS',`Hospital Research ID`)))/nrow(preds %>% filter(Status == 'P' &  !grepl('OCCAMS',`Hospital Research ID`))),2)

preds %>% dplyr::filter(Status == 'P' & !grepl('OCCAMS',`Hospital Research ID`)) %>% group_by(Risk) %>% tally() %>% spread(Risk, n) %>% 
  kable(caption=paste0('P risk predictions, FNR=',fnr)) %>% kable_styling(full_width = F) 
```

@@

# Non progressors
# FPR is ~40% still
fpr = round(nrow(preds %>% filter(Status == 'NP' & Risk == 'High'))/nrow(preds %>% filter(Status == 'NP')),2)

preds %>% dplyr::filter(Status == 'NP') %>% group_by(Risk) %>% tally() %>% spread(Risk, n) %>% 
  kable(caption=paste0('NP risk predictions, FPR=',fpr)) %>% kable_styling(full_width = F)

# Progressors
# FNR is still over 50% in the old progressors as well
fnr = round(nrow(preds %>% filter(Status == 'P' & Risk == 'Low' & !grepl('OCCAMS',`Hospital Research ID`)))/nrow(preds %>% filter(Status == 'P' &  !grepl('OCCAMS',`Hospital Research ID`))),2)

preds %>% dplyr::filter(Status == 'P' & !grepl('OCCAMS',`Hospital Research ID`)) %>% group_by(Risk) %>% tally() %>% spread(Risk, n) %>% 
  kable(caption=paste0('P risk predictions, FNR=',fnr)) %>% kable_styling(full_width = F) 
```
